Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-10 paper/pears.tex
results intro para, separations plot 1

%%%%%%%%%%%%%%%%%%%
%% dwarf figures %%
%%%%%%%%%%%%%%%%%%%

@@

\section{Results}
\subsection{Pair ratios}
Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.

@@

\subsection{Kinematic evolution}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is XX(XX) kpc, and peaks at $z=0$ with a median separation of XX (xx).
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is XX(XX), to $z=1$, where median separations are XX(XX). The median separation rises more steeply from z=1 to z=0, peaking at $z=0$ with median separations of XX and XX for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.  \todo{fill caption numberss, z=4, replace with 1000 reals plot}
    }
  \label{fig:sep}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. The distribution of velocities for major and minor pairs is roughly equivalent. 
  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals}
    }
  \label{fig:vel-dist}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%
%% dwarf figures %%
%%%%%%%%%%%%%%%%%%%
\kc{why did we stop at z=4? we didn't, explanation about low \# statistics }

@@

\section{Results}
We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation and analyze the occurrence rate and kinematic behavior of the pairs across cosmic time. 
At each snapshot, we generate 1000 different realizations of the pair catalog, where each realization represents one instance of the abundance matching technique to assign stellar masses to dark matter halos (see methods). 
In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values.

In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion/secondary, and compare the "pair fractions" of dwarf pairs and massive pairs.
In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the median separations and relative velocities between primary and secondary halos on a snapshot-by-snapshot basis.

\subsection{Pair fraction}\label{sec:results-frac}
Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.

@@

\subsection{Kinematic evolution}\label{sec:results-kinematics}
The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of

We separate the population of dwarf and massive pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-crit-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.

At each individual snapshot, we find the median separation

\subsubsection{Physical Separations}
The median separations of dwarf and massive pairs increases with lower redshift, regardless of pair type. 
Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type. 
Both dwarf and massive pairs have smoothly evolving medians that increase with decreasing redshift. 
There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$). 
Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.

Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$ for all 1000 AM realizations.

\subsubsection{Relative Velocities}
Fig.~\ref{fig:vel}
Fig.~\ref{fig:vel-dist}

%%% plots for kinematics
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The redshift evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
  At $z=4$, the typical separation between major (minor) dwarf pairs is XX(XX) kpc, and peaks at $z=0$ with a median separation of XX (xx).
  % Massive Pairs
  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is XX(XX), to $z=1$, where median separations are XX(XX). The median separation rises more steeply from z=1 to z=0, peaking at $z=0$ with median separations of XX and XX for major and minor massive pairs respectively.
  % Difference plots
  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.  \todo{fill caption numberss, z=4, replace with 1000 reals plot}
    }
  \label{fig:sep}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. The distribution of velocities for major and minor pairs is roughly equivalent. 
  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals}
    }
  \label{fig:vel-dist}
\end{figure*}
%%%
